\newpage
\section*{Exercises}

\begin{enumerate}	%main enumeration

\item Matrix calculations.

\be
 \item  Consider the matrix

\[
\bf A = 
 \left ( 
  \begin{array}{rr}
      1 & 2 \\
      2 & -4 \\
      4 & 6 \\
  \end{array}
 \right )
\]

Write the transpose of $\bf A$, the matrix $\bf A^T$.
 
 \item  Compute the result of multiplying $\bf A$ with the column
vector 
\[
v = 
 \left ( 
  \begin{array}{r}
    1 \\ 
    0 \\ 
   \end{array} 
 \right ).
\]
(that is, compute $\bf A v$).
 
 \item
Compute the result of multiplying $\bf A$ with the column
vector 
$\left ( \begin{array}{r} 1 \\ 1 \\ \end{array}  \right ) $.

 \item Compute the result of multiplying $\bf A$ with the column
vector 
\[
 \left ( 
  \begin{array}{r} 
   1  \\ 
   -1 \\ 
  \end{array}
 \right ).
\]
 
 \item Compute the result of multiplying $\bf A$ by the matrix

\[
\bf B = 
 \left (
   \begin{array}{rrr}
      1 & 1  & 1 \\
      0 & 1 & -1 \\
   \end{array}
 \right ).
\]

 \item How do the results of multiplying by the matrix compare with
the results of multiplying by the individual vectors?

 \ee

\item Answer the following questions about lens specifications.

 \be
 \item  When your eye doctor prescribes lenses for you, she tells you
the visual correction you require in terms of diopters.
What does it mean to require a 6-diopter optical correction?

 \item What does visual astigmatism mean?

 \item Do you think it is likely that different people
vary greatly in the extent of chromatic aberration in their eyes?
Why or why not?

 \item Suppose one individual needs a 6-diopter correction
and another individual needs a 3-diopter correction.
Give your best guess about the relative
linespread functions of the two individuals.
Give your best guess about the relative
modulation transfer functions of the two individuals.

 \ee

\item Answer these questions with respect
to experimental estimates
of the linespread function of the optics.

 \be

 \item What instrumentation might Campbell and Gubisch
have used to measure the pointspread function of the eye?
What additional problems would they have had if they
had measured the pointspread.
(See papers by Artal et al. (1989) for such measurements.)

 \item Can the linespread function be determined from the pointspread
function?  If so, how?

 \item Can the pointspread function be determined from a single
linespread function? If so, how?  
(See the appendix in Yellott, Wandell, and Cornsweet, 1980.)

 \item Do you think it is possible that Campbell and Gubisch
measured the light reflected precisely from the photoreceptor plane?
Why or why not?
If not, how should we evaluate the linespread function that we
estimate compared to the linespread function in the
plane of the photoreceptors?

\item IJspeert et al. (1993) recently described
a new set of equations to characterize the optical linespread of the
eye.
These equations are intended to generalize
Westheimer's function described in the text.
Read their paper and compare their new curves with
Westheimer's formula.

 \ee


\end{enumerate}	%main loop
