\documentstyle[12pt]{article}
\input{/home/brian/lib/tex/preamble}
\doublespace
\begin{document}

While preparing this book, I received generous and wise advice from
many people.  I am grateful to Tony Movshon for reading and commenting
on several chapters and answering many dozens of questions.  Dave
Marimont read large portions of the manuscript thoroughly and reminded
me what this book was about.  E. J. Chichilnisky, Joyce Farrell, and
David Heeger all spent many hours talking with me about aspects of
this book, and they shared their views on many issues ranging from
substance to style.  They were all patient and cheerful through an
endless series of interruptions, but I am sure that we are all relieved
this project is complete.

Many other individuals helped me either by reading and commenting on a
chapter, suggesting a figure, or working on some part of the
production process.  Their efforts were essential to whatever merit
this book may have.  Many thanks to J. Yellott, D. Williams,
D. MacLeod, D. Baylor, R. Rodieck, R. Shapley, S. Schein, D. Dacey,
H. Wassle, L. Silveira, J. Robson, P. Lennie, W. Newsome, J. Foley,
N. Graham, A. Watson, G. Legge, D. Fleet, E. Adelson, G. Phillips,
R. Born, D. Grossof, W. Geisler, A. Ahumada, A. Pentland, A. Poirson,
E. Simoncelli, D. Kelly, D. Kersten, D. Brainard, M. Shadlen,
P. Cavanagh, J. Mollon, K. Knoblauch, S. Kronzon, G. Boynton,
H. Hel-Or, V. Nalwa, S. Choi, P. Teo, S. Engel, E. Olds, X. Zhang

I am also grateful to David Brainard, Gordon Legge, Dan Kersten,
Jonathan Marshall and Stephen Pizer.  All of these brave people agreed
to teach from early versions of this book, and I benefited a great
deal from the comments they and their students provided.  In addition,
I wish to thank all of the students at Stanford who offered me
comments and encouragement during the years I taught from preliminary
versions of this book.  Their interest and enthusiasm for vision and
learning were an inspiration; their encouragement was often much
needed.

I am very grateful to Jan Ruby for the many different things she
has done during the last fifteen years to help me with this and 
other projects my laboratory .  Jan's diligence and good spirits
have been a wonderful help to me and all the members of my laboratory
who have had the good fortune to work with her.

Working with my editor, Peter Farley, has been a pleasure.  Thank you,
Peter, for your support and for being direct and helpful at all times.
And many thanks to your colleagues Kathaleen [LAST NAME] and Chris
[LAST NAME] at Sinauer Associates who worked so hard and so well to
help realize this book.

Several people arranged financial support so that I might suspend my
teaching and committee responsibilities at Stanford and concentrate on
writing.  I am grateful to Dave Marimont, Maureen Stone and John S.
Brown for arranging a one-quarter leave at Xerox Palo Alto Research
Center in 1992.  I am grateful to Gardner Lindzey and Robert Scott for
making a special effort to arrange a sabbatical year for me in 1988-89
at the Center for Advanced Study in the Behavioral Sciences.  During
that year this project and my son were born.

Thanks also to the many people on CVNET who responded to my electronic
query for useful numbers in vision science. A short list of numbers
connected to the material in this volume is contained within the front
cover of this book.  A much larger posting of their work can be found
on the world-wide web at the address: {\em
http://vision.arc.nasa.gov}.

Hagit Hel-Or and David Heeger took out time to create work with me to
create the cover image.  Thank you very much.  Working on the cover
gave us a chance to step back and see one big picture.  And a final
thanks to my son, Adam.  Whenever I become too absorbed in writing
this book, he reminded me that playing soccer, basketball, or taking a
bike ride to the park are important too, and this helped me to step
back and see another big picture.

\end{document}
